Wildcard: Spreadsheet-Driven Customization of Web Applications

### 2020-01-10 paper.tex
design tweaks

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

In this paper, we present \emph{spreadsheet-driven customization}, a
technique that enables end users to customize software. The idea is to
augment an application's UI with a spreadsheet that is synchronized with
the application's data. When the user manipulates the spreadsheet, the
underlying data is modified and the changes are propagated to the UI,
and vice versa. We have implemented this technique in a prototype
browser extension called Wildcard. Section 2 presents demos of using
Wildcard to augment real websites in useful ways, and Section 3
describes the implementation of the extension.

@@

Spreadsheet-driven customization provides an easy entry point for end
users, since small tweaks can be performed with a single click. At the
same time, it also supports a variety of richer customizations, like
adding private annotations to a webpage or joining in related data from
a web API. In Section 4, we elaborate on this principle of ``low floor,
high ceiling,'' as well as other design principles guiding our work.

@@

This approach requires extracting structured data from the user
interfaces of existing applications, but we hide the complexity of data
extraction from end users. Programmers write \emph{site adapters} which
use web scraping techniques to extract structured data from existing
applications and map them to the spreadsheet table. End users only
interact with the structured spreadsheet, providing a straightforward
customization experience. In Section 5, we explain this architecture in
more depth, and describe how Wildcard relates to existing work on
malleable software, web customization, spreadsheet-driven applications,
and web scraping.

@@

\hypertarget{demo-booking-a-trip-with-wildcard}{%
\section{Demo: booking a trip with
Wildcard}\label{demo-booking-a-trip-with-wildcard}}

@@

@@

Using Wildcard, the user can fix this omission, while leaving the page's
design and the rest of its functionality unchanged.{
fig.~\ref{fig:airbnb-demo} shows an overview of augmenting the Airbnb
site.} First, the user opens up the Wildcard panel, which shows a table
corresponding to the search results in the page. As they click around in
the table, the corresponding row in the page is highlighted so they can
see the connection between the views.

Then, the user clicks on the price column header to sort the
spreadsheet, and the Airbnb UI, by in ascending order by price{
(fig.~\ref{fig:airbnb-demo}B)}. They can similarly use the column
headers to filter to listings with a user rating above 4.5, which the
original Airbnb UI also doesn't allow.

@@

In the Airbnb UI, saving multiple listings to a Favorites list requires
tediously clicking through them one by one. Using Wildcard, the user can
select multiple rows and favorite all of them with a single click{
(fig.~\ref{fig:airbnb-demo}D)}. Similarly, the user can also open the
detailed pages for many listings at once.

Now the user wants to jot down some notes on the pros and cons of each
listing. To do this, they type some notes into an additional column in
each listing row, and the notes appear inside the listings in the
original UI{ (fig.~\ref{fig:airbnb-demo}A)}. The annotations are saved
in the browser for future sessions.

@@

When traveling without a car, it's useful to evaluate potential places
to stay based on how walkable the surroundings are. Using Wildcard
formulas, the user can integrate Airbnb with Walkscore, an API that
rates the walkability of any location on a 1-100 scale. When they type
in a \texttt{WALKSCORE} formula with the latitude and longitude of the
listing, it returns the walk score as the cell's value. Because the
cell's contents are injected into the page, the score also shows up in
the page body{ (fig.~\ref{fig:airbnb-demo}C)}.

@@

It might seem that Wildcard is only useful on websites that display
lists of tabular data like search results. But in fact, the table
metaphor is flexible enough to represent many types of data. For
example, a flight search form on Expedia can be represented as a single
row, with a column corresponding to each input. {
fig.~\ref{fig:expedia-demo} shows an overview of augmenting the Expedia
site.}

@@

Filling in dates for a flight search typically requires opening up a
separate calendar app to find the right dates and then manually copying
them into the form. In Wildcard, the user can avoid this cumbersome
workflow by using a datepicker widget that includes the user's personal
calendar information{ (fig.~\ref{fig:expedia-demo}B)}. The user can
directly click on the right date, and it gets inserted into the
spreadsheet and the original form.

@@

\hypertarget{system-architecture}{%
\section{System Architecture}\label{system-architecture}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\OperatorTok{\{}
\NormalTok{  fieldName}\OperatorTok{:} \StringTok{"name"}\OperatorTok{,} \CommentTok{// The name of the field}
\NormalTok{  type}\OperatorTok{:} \StringTok{"text"}\OperatorTok{,}      \CommentTok{// The type of the field}
\NormalTok{  readOnly}\OperatorTok{:} \KeywordTok{true}\OperatorTok{,}    \CommentTok{// Whether the user can edit the field}
\NormalTok{  el}\OperatorTok{:}\NormalTok{ (row) }\KeywordTok{=>} \VariableTok{row}\OperatorTok{.}\FunctionTok{querySelector}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}.}\SpecialCharTok{$\{}\NormalTok{titleClass}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{,} \CommentTok{// Extract DOM element}
\OperatorTok{\}}
\end{Highlighting}
\end{Shaded}

@@

\hypertarget{design-principles}{%
\section{Design principles}\label{design-principles}}

@@

\hypertarget{related-work}{%
\section{Related work}\label{related-work}}

>>>>

\hypertarget{sec:introduction}{%
\section{Introduction}\label{sec:introduction}}

@@

In this paper, we present \emph{spreadsheet-driven customization}, a
technique that enables end users to customize software. The idea is to
augment an application's UI with a spreadsheet that is synchronized with
the application's data. When the user manipulates the spreadsheet, the
underlying data is modified and the changes are propagated to the UI,
and vice versa. We have implemented this technique in a prototype
browser extension called Wildcard. Section~\ref{sec:demos} presents
demos of using Wildcard to augment real websites in useful ways, and
Section~\ref{sec:implementation} describes the implementation of the
extension.

@@

Spreadsheet-driven customization provides an easy entry point for end
users, since small tweaks can be performed with a single click. At the
same time, it also supports a variety of richer customizations, like
adding private annotations to a webpage or joining in related data from
a web API. In Section~\ref{sec:design-principles}, we elaborate on this
principle of ``low floor, high ceiling,'' as well as other design
principles guiding our work.

@@

This approach requires extracting structured data from the user
interfaces of existing applications, but we hide the complexity of data
extraction from end users. Programmers write \emph{site adapters} which
use web scraping techniques to extract structured data from existing
applications and map them to the spreadsheet table. End users only
interact with the structured spreadsheet, providing a straightforward
customization experience. In Section~\ref{sec:related-work}, we explain
this architecture in more depth, and describe how Wildcard relates to
existing work on malleable software, web customization,
spreadsheet-driven applications, and web scraping.

@@

\hypertarget{sec:demos}{%
\section{Demo: booking a trip with Wildcard}\label{sec:demos}}

@@

\hypertarget{customizing-search-results}{%
\subsection{Customizing search
results}\label{customizing-search-results}}

@@

Using Wildcard, the user can fix this omission, while leaving the page's
design and the rest of its functionality unchanged.{
Figure~\ref{fig:airbnb-demo} shows an overview of augmenting the Airbnb
site.} First, the user opens up the Wildcard panel, which shows a table
corresponding to the search results in the page. As they click around in
the table, the corresponding row in the page is highlighted so they can
see the connection between the views.

Then, the user clicks on the price column header to sort the
spreadsheet, and the Airbnb UI, by in ascending order by price{
(Figure~\ref{fig:airbnb-demo}B)}. They can similarly use the column
headers to filter to listings with a user rating above 4.5, which the
original Airbnb UI also doesn't allow.

@@

In the Airbnb UI, saving multiple listings to a Favorites list requires
tediously clicking through them one by one. Using Wildcard, the user can
select multiple rows and favorite all of them with a single click{
(Figure~\ref{fig:airbnb-demo}D)}. Similarly, the user can also open the
detailed pages for many listings at once.

Now the user wants to jot down some notes on the pros and cons of each
listing. To do this, they type some notes into an additional column in
each listing row, and the notes appear inside the listings in the
original UI{ (Figure~\ref{fig:airbnb-demo}A)}. The annotations are saved
in the browser for future sessions.

@@

When traveling without a car, it's useful to evaluate potential places
to stay based on how walkable the surroundings are. Using Wildcard
formulas, the user can integrate Airbnb with Walkscore, an API that
rates the walkability of any location on a 1-100 scale. When they type
in a \texttt{WALKSCORE} formula with the latitude and longitude of the
listing, it returns the walk score as the cell's value. Because the
cell's contents are injected into the page, the score also shows up in
the page body{ (Figure~\ref{fig:airbnb-demo}C)}.

@@

\hypertarget{customizing-a-form-input}{%
\subsection{Customizing a form input}\label{customizing-a-form-input}}

It might seem that Wildcard is only useful on websites that display
lists of tabular data like search results. But in fact, the table
metaphor is flexible enough to represent many types of data. For
example, a flight search form on Expedia can be represented as a single
row, with a column corresponding to each input. {
Figure~\ref{fig:expedia-demo} shows an overview of augmenting the
Expedia site.}

@@

Filling in dates for a flight search typically requires opening up a
separate calendar app to find the right dates and then manually copying
them into the form. In Wildcard, the user can avoid this cumbersome
workflow by using a datepicker widget that includes the user's personal
calendar information{ (Figure~\ref{fig:expedia-demo}B)}. The user can
directly click on the right date, and it gets inserted into the
spreadsheet and the original form.

@@

\hypertarget{sec:implementation}{%
\section{System Implementation}\label{sec:implementation}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\OperatorTok{\{}
  \CommentTok{// Field metadata:}
\NormalTok{  fieldName}\OperatorTok{:} \StringTok{"name"}\OperatorTok{,} \CommentTok{// The name of the field}
\NormalTok{  type}\OperatorTok{:} \StringTok{"text"}\OperatorTok{,}      \CommentTok{// The type of the field}
\NormalTok{  readOnly}\OperatorTok{:} \KeywordTok{true}\OperatorTok{,}    \CommentTok{// Whether the user can edit the field}

  \CommentTok{// Function to extract DOM element:}
\NormalTok{  el}\OperatorTok{:}\NormalTok{ (row) }\KeywordTok{=>} \VariableTok{row}\OperatorTok{.}\FunctionTok{querySelector}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}.}\SpecialCharTok{$\{}\NormalTok{titleClass}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{,}
\OperatorTok{\}}
\end{Highlighting}
\end{Shaded}

@@

\hypertarget{sec:design-principles}{%
\section{Design principles}\label{sec:design-principles}}

@@

\hypertarget{sec:related-work}{%
\section{Related work}\label{sec:related-work}}
